% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Yuntian Cui}

\basicInfo{
  \email{2206114057@stu.xjtu.edu.cn} \textperiodcentered\ 
  \phone{(+86) 18710326114}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Xi'an Jiao Tong University (XJTU)}, Xi'an, China}{2020 -- Present}
\textit{B.S.} in Software Engineering (SE)

\section{\faUsers\ Experience}

\datedsubsection{\textbf{TinyKV}}{Jul. 2023 -- Present}
\role{Golang}{Individual Projects from PingCAP Inc.}
Brief introduction: 
\begin{itemize}
  \item Standalone key-value storage system based on badger.
  \item RaftKV: high available kv server based on raft.
  \item MultiRaftKV: implemented control of many RaftKV groups. 
\end{itemize}

\datedsubsection{\textbf{Bustub}}{May. 2023 -- Jun. 2023}
\role{C++}{Individual Projects from CMU 15-445}
BusTub is an educational disk-oriented DBMS used for teaching database courses at Carnegie Mellon University.
\begin{itemize}
  \item Trie: a thread-safe data structure based on copy-on-write which can be read and written at the same time.
  \item Buffer pool based on K-LRU eviction algorithm.
  \item A part of query execution based on volcano and query optimization.
  \item Transaction manager: read uncommit, read commit, repeatable read isolation levels and dead lock detection.
\end{itemize}

\datedsubsection{\textbf{MIT/6.824 Distributed System}}{Oct. 2022 -- Dec. 2022}
\role{Golang}{Individual Projects from MIT 6.824}
labs from the course.
\begin{itemize}
  \item a simple MapReduce framework
  \item Raft algorithm
  \item RaftKV: high available kv server based on raft.
  \item ShardKV: multiple shard kv server based on hash distribution.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C/C++, Golang
  \item Development experience in EFI BIOS/Linux Kernel developing/EC FWs/Solari or other UNIX/Windows/Mac OS X.
  \item ISA: RISV-V
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
\datedline{Other awards}{2015}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: http://your.blog.me
  \item GitHub: https://github.com/username
  \item Languages: English - Fluent, Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
